\quad We are given an opportunity from our sponsor, Shawn N. Gieser to create a virtual theremin so we jumped onto this chance. This project was brought up from him during a meeting and we wanted this project. With this project is allows us to use our love for music to create a unique instrument that is not reliably available to most people. 

\quad A theremin, for those who do not know, is an instrument that does not require any touch, but it uses the players hand to change a magnetic field to create sound. When it comes to playing the user's non-dominant  hand is used to control the volume of the instrument while the dominant  is used to control the pitch. It both the sound and the act of playing the instrument is unique. Most people do not know what this instrument is and we would like to show a broader spectrum of people to it. 

\quad Since we want more people to be able to try out the theremin we want to allow for our software to be open to anyone. This will allow for anyone online to be able to grab our software and run it on there machine as long as they have a Leap Motion Controller 2. Our project exist to allow for any individual to be able to learn a theremin without the need to purchase one. We believe that the instrument should receive a lot more attention, but we understand that the issue with a real theremin is the cost of one it quite expensive. We can stop cost of entry this with our product making it cheaper than a real theremin.

\quad Along with making it cheaper we can use our project as a point of inspiration for the younger generation. Our sponsor has had the idea that we should make this project with the thought of kids involved so that this project is capable to show what people can do with computer science. This would an amazing example of what the world of computer science is capable and allow for a new generation of computer scientist. We feel as inspiring the next generation is more than enough of a reason for a project to exist cause it is like an art. We would like for our project to be show around the state of Texas. Our sponsor feels the same way as we do to our knowledge.

\quad Our sponsor is our teacher and we are their students. We have talked a little bit about the expectation from our project and has even recommend us our current hand tracker. We will be going to them for guidance when we need a guiding hand to help us along when we will needed. This is sorta of a dream project were we can work on something that allows for creative freedom and can inspire others into the same field that we fell in love with. 
