This section contains the approximate budget for the project, where that money will come from, and any other support. This text should be replaced with a discussion and justification of major expenses, but not the actual monetary amounts (that will go in the preliminary budget section below). 

Our budget is fairly cheap. Our main purchase will be the Leap Motion Controller 2 by Ultraleap. Since our project will require hand tracking to simulate a theremin, it will be easier to an existing hardware to keep track of the hand positions with IR. We are currently looking at Plastic SCM as an alternative to GitHub, as they have a limit of 2 GB for our plan. Only issue we can see is that Plastic SCM is a paid service for teams of 5, so we may need to discuss more if we were to migrate.

\subsection{Preliminary Budget}
Include a high level budget table for components, fabrication, software licensees, development hardware, etc. This should be in a tabular format broken up into appropriate line items. 
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Item} & \textbf{Description} & \textbf{Price}  \\ \hline
Leap Motion Controller 2 & IR Camera, tracks user hands. Made by Ultraleap & \$139  \\ \hline
Plastic SCM & Unity's Version Control. Paid monthly if ever used. & \$14  \\ \hline
\end{tabular}
\end{center}


\subsection{Current \& Pending Support}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Provider} & \textbf{Price}  \\ \hline
CSE department &  \$550  \\ \hline
Scott Frazier &  \$50  \\ \hline
Ron Nguyen &  \$50  \\ \hline
Farhan Sadiq &  \$50  \\ \hline
Sazzadul Islam &  \$50  \\ \hline
Caleb Myatt &  \$50  \\ \hline

\end{tabular}  
\end{center}
