Currently, we have no sponsors for our project other than our professor. Our team member consists of Scott Frazier, Ron Nguyen, Farhan Sadiq, Sazzadul Islam, and Caleb Myatt.

The stake holders in our project is our sponsor and teacher Shawn N. Gieser and the team including Scott Frazier, Ron Nguyen, Farhan Sadiq, Sazzadul Islam, and Caleb Myatt. Caleb is the point of contact to our sponsor. We will go about each individual what they want to do and take on that areas responsibility. 

Caleb will take on the role as the point of contact, and work on the coding side of the hands. What this will include with responsibilities is being able to contact with sponsor and telling our needs to him. Other responsibilities would also include getting the hand input from the user and converting that into our desired sounds. 

Ron will focus on working with the hand and the User Interface. This will include the responsibilities of converting the hand input from the user and converting  that into our desired sounds. Also they will be creating an interface for the end user to be able to interact with our software. 

Farhan will also focus on the coding aspects of the hands. This will include mostly backend work. He will also be assisting in any documentation work required for the project.

Sazzadul will also be focusing on coding and testing aspects of the project. This will include collaborating with the team on the coding aspects, particularly focusing on specific features or functionalities that require development and testing. Also, contribute with the team members for any documentation needed for the project.    

Scott will be focusing on documentation and testing of the hands. This will include talking to the team and understanding the project as a whole. The testing of the hands will be manually to ensure a good end user experiance. 

Our scrum master will change periodically when we feel like there is a need of change so that we can take a different approach. 
